---
title: "RXY Package Description"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Plot_Function-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(rxy)
```

Welcome to the RXY Package

This package allows a user to be able to see the correlations between a dependent
variable in a dataset and either an individual dependent variable or multiple dependent
variables. There are different functions that allow for a user to be able to look at 
the correlations. The plot function allows the correlations to be seen visually. The 
print function allows the correlations to be seen in a chart. The summary function does not allow for all individual correlations to be seen, but provides a short script which contains what variables were looked at along with the range for the correlations, the median of the correlations, and how many variables had significant p-values. 








